Timeliness of security updates for Android

### 2014-08-12 security_scoring.tex
Remove mcalculation table and expand the caption text instead

\begin{figure}
\centering
%\includegraphics[width=\columnwidth]{figures/mcalculation}
\include{figures/mcalculation}
\begin{tabular}{c|c|c}
active vulnerabilities & \# days & percent\\
\hline
0 & 3 & 15\%\\
1 & 5 & 25\%\\
2 & 10 & 50\%\\
3 & 2 & 10\%\\
\hline
\hline
$m$ & \multicolumn{2}{c}{1.55}\\
MAV & \multicolumn{2}{c}{2}\\
VFD & \multicolumn{2}{c}{15\%}\\

\end{tabular}
\caption{Example $m$ calculation based on the one given in by Wright~\cite{Wright2014} giving MAV and VFD for comparison.}
\label{fig:mcalculation}
\end{figure}

>>>>

\begin{figure}
\centering
%\includegraphics[width=\columnwidth]{figures/mcalculation}
\include{figures/mcalculation}
\caption{As vulnerabilities are discovered and patched the sum of known but unpatched vulnerabilities each day varies. From this we can calculate $m = (0 \times 3 + 1 \times 5 + 2 \times 10 + 3 \times 2) / 20 = 1.55$ For comparison VFD = 0.15 and MAV = 2. Example based on the one given by Wright~\cite{Wright2014}.}
\label{fig:mcalculation}
\end{figure}
